Now, it's time for Words and Their Stories, a program from VOA Learning English.
现在是美国之音慢速英语词汇掌故节目时间。
The internet has taught us many things. One important lesson is this: Cats are funny, strange and often unpredictable animals. Their quirky personalities have made cats popular as household pets in homes across the United States.
互联网教会了我们很多东西。其中一个重要教训就是：猫是一种有趣、奇怪而且往往不可捉摸的动物。这种古怪个性使得猫成为了全美国最受欢迎的家庭宠物。

And they are great hunters. Mice are often on their top five kill list. But sometimes, a cat will not kill the animal it catches. Instead, the catch becomes kind of a toy or plaything.
同时它们是伟大的捕手。老鼠通常是它们消灭名单的前五位。但是有时候猫不会吃掉它们抓到的动物。相反，猎物会变成它们的玩物。

The cat seizes a mouse. Then lets it go. Catches it. Lets it go. Over and over again! It is good fun for the cat but frightening for the poor mouse.
猫抓住老鼠，然后放掉，再抓住，再放掉，就这样一遍遍重复。对猫来说这很好玩，对可怜的老鼠来说却是恐惧。

So, if you play cat and mouse with someone, you play a power game with them. You, the person with the power, are the cat. Maybe you pretend to give the other person something they want but then take it away. You toy with them. We often call a situation like this a cat-and-mouse game. For example, a child might offer something sweet to her little brother and then take it away when he reaches for it.
因此，如果你和某人玩猫鼠游戏，意思是你跟他们玩权力游戏。你作为有权势的一方，就是猫。可能你会假装给某人他们想要的东西，然后又将其拿走。你在玩弄他们。我们通常称这种情况是猫鼠游戏。例如，某个孩子可能会给她弟弟一些甜食，然后在弟弟伸手要够时又把它拿走。

A cat-and-mouse game is filled with lots of action: chases, near captures and repeated escapes. In extreme cases, a cat-and-mouse game is never-ending.
猫鼠游戏有很多动作：追逐、近距离捕获以及反复逃跑。在某些极端情况下，猫鼠游戏永远没有结束的时候。

Now, let's leave the game of cat and mouse and talk about playing in a different way.
现在让我们放下猫鼠游戏，谈谈另一种玩法。

Let's imagine a classroom filled with young children. The teacher must leave the room for a couple of minutes. At first, everyone is well-behaved. But the longer the teacher is gone, the more the class acts up. It starts out slowly. Someone throws a piece of paper. A couple of students get up and walk around. Others start laughing loudly. Someone yells! Suddenly, all of the students are doing things they would never do with the teacher in the room.
我们假设一个教室里坐满了小孩子。老师必须离开教室几分钟时间。起初每个人都表现得很棒。但是老师离开的时间越长，班上捣蛋的就越多。它是慢慢开始的。有人扔了一张纸，几个学生站起来到处走。其他人开始大声说笑。有人大喊。突然，所有学生都在做老师在教室时他们永远不会去做的事情。

But you know what we say: When the cat's away, the mice will play!
但是你知道我们说的：猫儿不在，老鼠成精。

This expression means that people sometimes misbehave when no one is there to watch them. So, the teacher is the cat and the students are the mice.
这句表达的意思是有时候人们在没管的时候会乱来。所以，老师就是猫，学生们是老鼠。

We often use this expression when talking about children and parents, employees and office supervisors and even people in committed relationships.
我们在谈论孩子和父母，员工和领导，以及存在固定关系的人们时常常会用到这句表达。

And that brings us to the end of this Words and Their Stories.
以上就是本期词汇掌故节目的全部内容。

Until next time ... I'm Anna Matteo.
我们下次节目再会。我是安娜·马特奥。

(51VOA.COM原创翻译，禁止转载，违者必究！)

