\href{https://www.51voa.com/VOA_Special_English/program-collects-smartphones-for-coronavirus-hospital-patients-to-use-84557_1.html}{Article Translate} \\

It is one of the many cruelties of the pandemic. To prevent the spread of the coronavirus, many people hospitalized with COVID-19 cannot have visitors. This means the patients are unable to celebrate life events with loved ones – or even say a final goodbye.
这是大流行下的许多惨剧之一。为了防止新冠病毒传播，许多因为新冠肺炎住院的患者都不能接受探视。这意味这些患者无法与亲人一起庆祝人生大事，甚至无法道一声永别。
Kaya Suner came up with a solution. The 19-year-old from Rhode Island found a way to collect used smartphones and tablets and get them to patients suffering from the disease. The devices can help the patients communicate with their friends and family.
卡亚·苏诺提出了一个解决方案。这位来自罗德岛州的19岁男孩找到了一种办法，收集人们用过的智能手机和平板电脑，并把它们带给新冠肺炎患者。这些设备可以帮助患者与他们的家人和朋友交流。

His idea has started to spread.
他的想法开始传播开来。

"Kaya, you're 19, but you're a superstar, you're a hero," Rhode Island Governor, Gina Raimondo, said at a news conference in April. Raimondo's son donated an iPad to the cause.
罗德岛州州长吉娜·雷蒙多在4月份的一场新闻发布会上说：“卡亚，你只有19岁，但是你是超级巨星，你是英雄。”雷蒙多的儿子为此捐献了一台iPad。

The idea came from Suner's desire to help. He considered making protective face coverings. But his parents, both emergency room doctors, inspired him to do more.
这个想法来自于卡亚助人的意愿。他考虑过制作防护面罩。但是他的父母都是急诊室医生，他们激发他做更多事情。

One day, Suner was talking online with his mother, who is living separately from her son because her job puts her at a higher risk of getting sick. His mother told him that many of her patients are old and have no way to stay in touch with loved ones while they are hospitalized. Feelings of loneliness are common among the patients.
有一天，苏诺跟他母亲在网上聊天，这位母亲与儿子分开住，因为她的职业让她有很高的感染风险。他的母亲告诉他，很多患者年纪较大，在住院期间无法跟亲人保持联系。孤独感在这些患者中很常见。

"There's no way for these sick patients to communicate with their loved ones due to the visitation ban in hospitals," Suner said. "It's really unfortunate that that's what's going on..."
苏诺表示：“由于医院的探视禁令，这些患者无法与亲人交流，发生这种事情真不幸。”

So, he and a friend asked for donations of used smartphones and tablets to give to those patients.
所以，他和一位朋友请求人们把用过的智能手机和平板电脑捐献给这些患者。

They started with a simple request on Facebook. That effort developed into covidconnectors.org. The website lets people donate "gently used" devices that can record video.
他们一开始在脸书网上发出了一个简单的请求。这项努力最终发展成了covidconnectors.org这个网站。该网站让人们捐献可以录制视频的二手设备。

Patients have used the donated devices for everything from celebrating birthdays and meeting new grandchildren to saying final goodbyes, Suner said.
苏诺表示，患者们使用这些捐赠的设备做了各种事情，从庆祝生日，到见刚出生的孙子，到说永别。

"One family member said that they had someone in the hospital who wanted their last rites read," he said. "We were able to get an iPad to them..."
他说：“有位家人说，他们医院曾经有人想做临终祈祷。我们把iPad带给了他们。”

The program has been a success. In fact, the needs of Rhode Island's coronavirus patients have been met. The program is now collecting devices for medical centers in nearby Massachusetts and New Hampshire. Suner hopes to expand into New York soon.
这个项目取得了成功。实际上，罗德岛州新冠病毒患者的需求得到了满足。该项目现在正在为邻近的马萨诸塞州以及新罕布什尔州的医疗中心收集设备。苏诺希望很快将该项目扩大到纽约州。

He is concerned that as some states start to reopen, people will think there is no need for donations. But, he said, that is not the case.
他担心随着一些州开始重新开放，人们会认为没有必要捐赠。但是他说，事实并非如此。

"This is still a really, really large issue inside of hospitals," he said.
他说：“这在医院内部仍然是一个非常大的问题。”

I'm Ashley Thompson.
我是阿什利·汤普森。(51VOA.COM原创翻译，禁止转载，违者必究！)
