\href{https://www.51voa.com/VOA_Special_English/researchers-call-for-a-use-tax-to-clean-up-space-84650_1.html}{Article Translate} \\
Orbital structures are becoming increasingly important for worldwide communications and a new generation of technologies. But scientists are warning that the danger of space debris is increasing very quickly.
轨道装置对于全球通信和新一代技术变得越来越重要。但是科学家们警告说，太空碎片形成的风险正在迅速增加。 
Space debris can include pieces of old rockets, non-operational satellites, lost tools and other parts. These pieces of wreckage present a risk to spaceships, satellites and space stations.
太空碎片可能包括老火箭碎片、报废卫星，丢失的工具和其它零部件。这些碎片对飞船、卫星和空间站都构成风险。
In an effort to reduce the amount of debris orbiting the Earth, some experts suggest creating "orbital-use fees."
为了减少环地球运行的碎片数量，一些专家建议增设“轨道使用费。”
A group of economists at the University of Colorado at Boulder proposed a yearly fee, or tax, on satellite operators for their use of an orbital path. The group's study on the subject appeared recently in the publication Proceedings of the National Academy of Sciences.
科罗拉多大学博尔德分校的一组经济学家建议，对卫星运营商使用轨道收取年度费用或税款。该小组就该主题的研究最近发表在《美国国家科学院院刊》上。
Matthew Burgess helped write the study. He said in a statement: "Space is a common resource, but companies aren't accounting for the cost their satellites impose on other operators when they decide whether or not to launch."
马修·伯吉斯协助撰写了这份研究报告。他在一份声明中表示：“太空是一种公共资源，但是各家公司决定是否发射时，并未考虑他们的卫星给其它运营商带来的成本。”
Burgess added, "We need a policy that lets satellite operators directly factor in the costs their launches impose on other operators."
伯吉斯还说：“我们需要出台一项政策，让卫星运营商直接纳入其发射给其它运营商带来的成本。”
The researchers said current rules do not permit satellite operators to secure property rights to orbital paths high above the Earth. Other operators also do not have to pay for costs related to incidents involving space debris, the researchers noted.
研究人员表示，现有规定不允许卫星运营商获得地球以上轨道的产权。研究人员指出，其它运营商也无需承担与太空碎片相关事故的费用。
The study said that this situation gives companies a reason to quickly launch into Earth orbit before it gets too crowded.
该研究称，这种情况使得各公司有理由在轨道变得过于拥挤之前迅速进入地球轨道。
Akhil Rao was the lead writer of the study. He said most proposed answers to the problem have been based on using technology to clear away the debris. Some suggestions, for example, call for nets or other devices that capture the space wreckage.
阿基尔·劳是这项研究的主要作者。他说，针对该问题的大多数提议都是基于使用技术清除碎片。例如，有人建议使用网或其它设备捕获太空残骸。
But, Burgess said that removing debris only means that operators will launch more satellites.
但是伯吉斯表示，清理碎片只会意味着运营商将发射更多卫星。
He said an international treaty calling for a yearly fee or tax would push companies to be more mindful about launching more objects into space.
他说，出台一项要求收取年度费用或税款的国际条约将促使各公司向太空发射更多物体会更加谨慎。
Holger Krag heads the European Space Agency's Space Debris Office. He called the idea "interesting" and said his agency was studying similar possibilities. ESA was also considering ways to account for the environmental costs of space operations.
霍尔格·克拉格负责欧洲航天局的太空碎片办公室。他称这个想法非常有趣，并称该机构正在研究类似的可能性。欧洲航天局正在考虑核算太空业务环境成本的方法。
Christopher Newman is a professor of space law at Northumbria University in Britain. He told the Thomson Reuters Foundation that carrying out a space tax could be tricky.
克里斯托弗·纽曼是英国诺森比亚大学的太空法教授。他对汤普森路透基金会表示，征收太空税可能很棘手。
Newman noted that such a cost could be seen as a restriction on the free use of space. That freedom is guaranteed in the Outer Space Treaty of 1967. The United Nations document has been signed by more than 100 nations.
纽曼指出，这种费用可以看作是对自由利用太空的限制。这种自由受到《1967年外层空间法》的保障。这个联合国文档已经由一百多个国家签署。
Newman added that the effort to place a fee on the use of space could easily be slowed by the many details involved.
纽曼还说，其中涉及的诸多细节可能会轻松拖慢对太空利用收费的努力。
I'm Mario Ritter Jr.
我是小马里奥·里特。(51VOA.COM原创翻译，禁止转载，违者必究！)
