Big companies are trying to keep their employees healthy by banning business trips. The decision, however, has been a hard blow to the travel industry, which has already been suffering because of the effects of the new coronavirus.
大型企业正试图通过禁止商务旅行来确保员工的健康。但是这一决定给已经因为新型冠状病毒遭受重创的旅游业造成了沉重打击。
Amazon, the American-based online business, has told its nearly 800,000 workers to postpone any unnecessary travel within the United States or around the world.
总部位于美国的网络公司亚马逊已经通知其近80万员工推迟在美国国内或全球范围内任何非必要的旅行。

Swiss food company Nestle told its 291,000 employees worldwide to limit local business travel and stop all international travel until March 15.
瑞士食品公司雀巢通知该公司在全球的29.1万名员工，在3月1日前要限制当地商务旅行并停止所有全球旅行。

France's L'Oréal, maker of beauty products, employs 86,000 people. It has announced a travel ban until March 31.
法国美容产品制造商欧莱雅公司雇用了8.6万名员工。该公司宣布3月31日前禁止旅行。

Major business gatherings, like the Mobile World Congress in Barcelona, have also been canceled.
诸如巴塞罗那世界移动大会之类的大型商业聚会也都被取消。

On Tuesday, Facebook confirmed it will not attend the South by Southwest conference in Austin, Texas. The event is supposed to start on March 13.
周二，脸书网确认将不会参加在德克萨斯州奥斯汀市举行的西南偏南大会。该活动原定于3月13日开幕。

In addition, the International Monetary Fund and the World Bank have announced they will replace their spring meetings in Washington with an online event.
此外，国际货币基金组织和世界银行宣布将通过线上活动替代他们在华盛顿的春季会议。

Robin Ottaway is president of Brooklyn Brewery. He canceled a trip to Seoul and Tokyo last week. He has suspended all travel to Asia and canceled a planned trip this month to Copenhagen.
罗槟·奥特韦是布鲁克林啤酒厂的总裁。他上周取消了前往首尔和东京的旅行。他已经暂停前往亚洲，并取消了本月原计划前往哥本哈根的旅行。

"I wasn't worried about getting sick. I'm a healthy 46-year-old man," Ottaway said. "My only worry was getting stuck in Asia or quarantined after returning to the U.S. And I'd hate to be a spreader of the virus."
奥特韦表示：“我不是害怕感染。我是一位46岁的健康男性。我唯一担心是被困在亚洲，或是回到美国后被隔离。我不想成为这种病毒的传播者。”

Effect on business travel
对商务旅行的影响

The cancellations and travel restrictions are hurting the travel industry. Business travel makes up around 26 percent of the total travel spending, or around $1.5 trillion per year, notes the Global Business Travel Association.
取消和旅行限制伤害了旅游业。全球商务旅行协会指出，商务旅行约占整个旅行支出的26%，即每年大约1.5万亿美元。

The association estimates the virus is costing the business travel industry $47 billion per month.
该协会估计该病毒每个月给商务旅行行业造成470亿美元的损失。

"It's a big deal," said Henry Harteveldt, a travel industry expert. He estimates that airline companies get 55 percent of their money from business travelers because they often sit in pricier business or first-class seats.
旅游行业专家亨特·哈特威尔特表示：“这是个大事件。”他估计航空公司55%对收入来自于商务旅客，因为他们通常乘坐价格更高的商务舱或头等舱。

Numbers from the Airlines Reporting Corporation show that airline ticket sales fell about 9 percent in late February, compared with a year earlier.
航空报告公司的数据显示，与去年同期相比，2月下旬的机票销售下降了大约9%。

Hotel operators are also worried about decreases in business travel. In the United States, hotels are expected to earn $46 billion from business travel this year, said the travel research service Phocuswright. No one believes that is possible now.
酒店经营者也在担心商务旅行的减少。旅游研究公司Phocuswright表示，美国酒店今年预计从商务旅行中赚到460亿美元。现在没人相信这能实现。

In the week through February 22, hotel occupancy rates in San Francisco were down 11 percent, noted STR, a company that researches hotel usage. Several major companies pulled out of the city's cybersecurity conference, which began in February.
研究酒店入住率的STR公司指出，截至2月22日的这个星期，旧金山酒店入住率下降了11%。几家重要公司退出了该市2月份开始举行的网络安全会议。

Some observers say it is wise for companies to postpone or cancel travel before things get worse. Worldwide, the coronavirus has sickened over 90,000 people. More than 3,000 have died from COVID-19, the disease resulting from the virus.
一些观察人士表示，企业在情况恶化前取消或推迟旅行是非常明智的。在全球范围内，这种冠状病毒已经导致9万人感染。超过3千人因为这种病毒引起的新型冠状病毒肺炎死亡。

Kevin Mitchell is chairman of the Business Travel Coalition. He is an expert in the ways large companies and governments can control travel costs. He notes that if a company puts an employee at risk, "you can be held responsible for their injury or death."
凯文·米切尔是商务旅行联盟的主席。他是大型企业和政府差旅成本控制方面的专家。他指出，如果企业将员工置于危险之中，“可能需要对他们的伤亡负责。”