\href{https://www.51voa.com/VOA_Special_English/us-border-falls-quiet-with-millions-of-mexicans-barred-84264_1.html}{Article Translate} \\
The world's busiest land border has fallen quiet. Restrictions meant to contain the spread of the new coronavirus have stopped millions of Mexicans from making daily trips north to the United States. That includes many who work at U.S. businesses.
全球最繁忙的陆地边界已经安静了下来。旨在遏制新冠病毒传播的限制措施阻止了数百万墨西哥人每天北上美国。其中包括许多在美国企业工作的人士。
At least 4 million Mexicans who live in cities along the 3,144-kilometer-long border have been affected by the restrictions on travel. The measures do not permit short crossings into American cities to visit family, get medical care or buy goods.
至少有400万居住在3144公里长边境沿线城市的墨西哥人受到了旅行限制措施的影响。这些措施禁止短期过境进入美国城市探亲、看病或是购物。

Many of those affected have legal "border crossing cards," which are for meant visits not related to work. Reuters reporters spoke to more than 20 people who live in Tijuana, Nogales and Ciudad Juarez. Most use their cards to care for family members on the U.S. side of the border. Some use them to work illegally.
许多受影响者都拥有合法的过境卡，用于与工作无关的访问。路透社记者采访了居住在蒂华纳、诺加莱斯和华雷斯城的20多位人士。他们大多数人使用过境卡照顾美国一侧的家人。也有人利用它非法打工。

All of those who spoke with the reporters said they could no longer make the crossing. This has also affected businesses on the U.S. side of the border that hire them – illegally – for agricultural jobs.
接受该记者采访的所有人都表示，他们不能再过境。这也影响到了美国一侧非法雇佣他们从事农业工作的企业。

"I don't know what I'm going to do without money. I'm just waiting for a miracle," said 28-year-old Rosario Cruz. She is a mother of two young children and works for a cleaning company.
28岁的罗萨里奥·克鲁兹表示：“我不知道没钱了我该怎么办，我只能等着发生奇迹。”她是两个孩子的母亲，在一家清洁公司工作。

The coronavirus restrictions have stopped all non-essential travel across the border. However, the restrictions do not stop Americans from going to Mexico.
冠状病毒限制措施已经阻止了所有不必要的跨境旅行。然而，这些限制措施并未阻止美国人去墨西哥。

The U.S. Immigration and Customs Enforcement agency said it did not have an estimate of how many Mexicans with border crossing cards work illegally in the United States. But U.S. and Mexican immigration experts believe the number is high.
美国移民和海关执法局表示，它并未估算有多少墨西哥人持过境卡在美国非法打工。但是美国和墨西哥的移民专家都认为这个数字非常高。

The U.S. State Department says more than 4 million border cards have been issued since 2015. The cards can be used for 10 years.
美国国务院表示，自2015年以来已经发放了超过4百万张过境卡。这些卡的有效期是10年。

Before the coronavirus restrictions, more than 950,000 people entered the United States from Mexico every day. That information comes from the U.S. Customs and Border Protection (CBP) agency.
在出台冠状病毒限制措施之前，每天有超过95万人从墨西哥进入美国。该信息来自于美国海关与边境保护局。

Andrew Selee is president of the Migration Policy Institute, based in Washington, D.C. He said limiting border crossing to fight the pandemic was understandable. But he worries that in cities such as San Diego, California, or El Paso, Texas, "businesses that really should be open in the middle of a crisis might find that they don't have employees."
安德鲁·塞利是华盛顿特区移民政策研究所的所长。他表示，限制过境以对抗大流行是可以理解的。但是他担心，在加州圣地亚哥或德州埃尔帕索这样的城市，“在危机中确实应该开放的企业可能会发现他们没有员工。”

"We're talking about farm work, we're talking about caregiving," he said.
他说：“我说的是农业和护理方面的工作。”

In U.S. border cities like El Paso and San Diego, the effects are already being felt.
在埃尔帕索和圣地亚哥这样的美国边境城市，这种影响已经显现出来。

Cindy Ramos-Davidson is the chief executive of the El Paso Hispanic Chamber of Commerce. She said the lack of Mexican shoppers was "devastating" for small businesses downtown. She was also concerned about the nearby farms that use Mexican workers.
辛迪·拉莫斯-戴维森是埃尔帕索西班牙裔商会的首席执行官。她说，缺少墨西哥购物者对于市区的小企业来说是“毁灭性的”。她还担心附近雇佣墨西哥工人的农场。

"They depend on farm workers, the day workers," she said. She noted that many of these workers use their cards to work in the U.S. illegally.
她说：“他们依赖打散工的农场工人。”她指出，其中多数工人使用过境卡在美国非法打工。

Paola Avila is a vice president of the San Diego Regional Chamber of Commerce. She said the city's so-called retail tourism has been badly affected. Retail tourism describes money spent by Mexicans who cross the border to buy certain goods.
宝拉·阿维拉是圣地亚哥地区商会的副会长。她说，该市的零售旅游业受到了严重影响。零售旅游业描绘了墨西哥跨境购买特定商品所花费的资金。

Avila is also worried about the effect on U.S. citizens who are cared for by family members who cross from Mexico.
阿维拉还担心由墨西哥跨境进入美国的家人所照顾的美国公民的生活受到影响。

"If the hospitals overflow, as we predict, and they start sending people to be cared for at home, who will care for them?" she asked.
她问道：“如果医院如我们所预料的爆满，然后他们开始把人们送回家来照料，那么谁来照顾他们呢？”

I'm John Russell.
我是约翰·罗素。(51VOA.COM原创翻译，禁止转载，违者必究！)
