\href{https://www.51voa.com/VOA_Special_English/sanders-ends-campaign-biden-likely-to-face-trump-84288_1.html}{Article Translate} \\

United States Senator Bernie Sanders ended his presidential campaign on Wednesday. The move leaves former Vice President Joe Biden as the likely Democratic Party nominee to face President Donald Trump in November. Trump belongs to the Republican Party.
美国参议员伯尼·桑德斯周三退出了总统竞选。此举使得前副总统乔·拜登成为可能在今年11月与川普对决的民主党候选人。川普属于共和党。
The Vermont senator told supporters, "I have concluded that this battle for the Democratic nomination will not be successful. And so today, I am announcing the suspension of my campaign." Sanders praised Biden as "a very decent man." The senator said he would work with the likely nominee "to move our progressive ideas forward."
桑德斯这位佛蒙特州参议员对支持者表示：“我得出的结论是，这场争取获得民主党提名的战斗不会成功。所以今天我宣布中止竞选。”桑德斯称赞拜登是一位“非常正派的人。”这位参议员表示，他将与这位潜在提名人一起，“推动我们的进步思想向前发展。”

Biden thanked Sanders on Twitter for putting "the interest of the nation – and the need to defeat Donald Trump – above all else."
拜登在推特上感谢桑德斯“将国家利益以及击败川普的需求放在首位。”

In an appeal to Sander's supporters, Biden wrote "I know that I need to earn your votes. And I know that might take time. But I want you to know that I see you, I hear you, and I understand the urgency of this moment. I hope you'll join us. You're more than welcome: You're needed."
拜登在向桑德斯支持者的喊话中写道：“我知道我需要赢得你的选票。我也知道这可能需要时间。但是我希望你知道，我看见你，听见你，而且我了解这样做的紧迫性。希望你能加入我们。我们不止是欢迎你：我们需要你。”

President Donald Trump reacted to the announcement with a message on Twitter. It said that the nomination race had ended just the way the Democratic Party wanted.
川普总统在推特上对此消息作出了回应。该推文称，总统提名竞争已经按照民主党想要的方式结束了。

"The Bernie people should come to the Republican Party, TRADE!" he added.
川普还表示：“桑德斯的支持者应该加入共和党。”

Sanders was the early leader in the race for the Democratic presidential nomination in 2020.
桑德斯是2020年民主党总统提名竞选中早期的领先者。

He received firm support from young people and non-professionals. He seeks free college education, cancellation of current student loan debts, and free healthcare for Americans. He also calls for passage of the "Green New Deal," a Democratic Party proposal designed to deal with climate change.
他得到了年轻人和非专业人士的坚定支持。他主张免除大学学费，取消目前的学生贷款债务以及为美国人提供免费医保。他还呼吁通过“绿色新政”，这是民主党旨在应对气候变化的提案。

The Vermont senator won the nominating elections in Iowa, New Hampshire and Nevada.
这位佛蒙特州参议员赢得了爱荷华州、新罕布什尔州和内华达州的提名选举。

After Joe Biden's first victory in the state of South Carolina, others in the race, as well as Democratic Party leaders, announced their support for Biden's nomination. That helped Biden win many primaries that followed, including 10 out of 14 states on Super Tuesday.
拜登在南卡罗莱纳州取得首场胜利之后，其它候选人以及民主党领导人宣布支持拜登。这帮助拜登赢得了随后的许多场初选，包括超级星期二在14个州中赢得了10场胜利。

The coronavirus outbreak effectively put a stop to official campaigning by the candidates. Primaries have been postponed or cancelled in many states.
冠状病毒的爆发有效地阻止了候选人的正式竞选活动。在许多州，初选已经被推迟或取消。

Sanders announced his decision Wednesday from his hometown of Burlington, Vermont. He said, "Standing united, we will go forward to defeat Donald Trump, the most dangerous president in modern American history."
桑德斯周三在他的家乡佛蒙特州伯灵顿宣布了他的决定。他说：“坚定团结，我们将继续击败川普这位美国现代史上最危险的总统。”

I'm John Russell.
我是约翰·罗素。(51VOA.COM原创翻译，禁止转载，违者必究！)
