\href{https://www.51voa.com/VOA_Special_English/moderna-says-early-coronavirus-vaccine-shows-promise-84567_1.html}{Article Translate} \\

American drug maker Moderna said Monday that its experimental COVID-19 vaccine produced antibodies in a small group of healthy people in an early trial.
美国制药商现代公司周一表示，其试验性新冠肺炎疫苗在早期试验的一小群健康人群中产生了抗体。
The company said eight people who received two small amounts of its vaccine developed antibodies similar to those developed by people who have recovered from the disease.
该公司表示，8名接受两种小剂量疫苗注射的人士产生了与新冠肺炎康复者相似的抗体。

The U.S. National Institute of Allergy and Infectious Diseases led the experiment, also called a trial. It involved 45 volunteers who received one or two shots of differing amounts of the vaccine.
美国国家过敏与传染病研究所主导了这项试验。其中有45名志愿者接受了一到两针不同剂量的疫苗。

Tal Zaks is the chief medical officer at Moderna. Based on early results of the trial, he said the vaccine "has the potential to prevent COVID-19 disease...." He also said the company now can better choose the vaccine amount needed for further experiments.
塔尔·扎克斯是现代公司的首席医疗官。他说，根据试验早期结果，疫苗“具备了预防新冠肺炎的潜力。”他还表示该公司现在可以更好地选择进一步试验所需的疫苗剂量。

The testing involved three different amounts. Zaks said the two smaller amounts of vaccine seem safe and the larger amount caused some short-term side effects. Three study subjects developed "flu-like" conditions following a second shot of the large dose. Moderna said it plans to drop that amount for the next part of the trial.
这次试验涉及了三种不同的剂量。扎克斯表示，两种较小剂量的疫苗似乎是安全的，而较大剂量的疫苗会产生一些短期的副作用。有3名试验对象在大剂量疫苗的第二次注射之后出现了“流感样”症状。现代公司称其计划在下阶段试验中放弃该剂量。

Amesh Adalja is an infectious disease expert at the Johns Hopkins Center for Health Security who was not involved in the study. He told Reuters that the findings are meaningful, but noted that they come from only eight people. "It was designed for safety. Not for efficacy," he said.
阿梅什·阿达贾是约翰·霍普金斯大学健康安全中心的一名传染病专家，他没有参与这项研究。他对路透社表示，这些发现很有意义，但是他指出这些发现仅来自于8个人。他说：“它的设计是为了安全，而不是为了功效。”

Moderna has been permitted to start a second part of human testing that will involve several hundreds of people. In April, the U.S. government gave the company \$483 million for vaccine development. Last week, U.S. officials gave the vaccine special recognition to help speed the process for approval.
现代公司已经获准进行涉及数百人的第二阶段人类试验。今年4月，美国政府为该公司提供了4.83亿美元的疫苗开发资金。上周，美国官员对该疫苗进行了特别认证以帮助加快其获批程序。

Stéphane Bancel, Chief Executive Officer of Moderna, said the company is hoping to start part three of the study in July. The company will try to find the lowest amount of vaccine necessary to protect people.
现代公司首席执行官斯蒂凡·班塞尔表示，该公司希望在7月份开始第三阶段研究。该公司将尝试找出保护人类所需的最低疫苗剂量。

In May, Moderna and the biotechnology company Lonza agreed to work together over the next ten years to make a vaccine. The partnership could lead to the manufacture of 1 billion COVID-19 vaccine treatments a year.
今年5月，现代公司和龙沙生物技术公司同意在未来10年内联合生产疫苗。该伙伴关系可能会导致每年生产出10亿份新冠肺炎疫苗。

There are currently no approved treatments or vaccines for COVID-19. Almost 4.8 million people are confirmed to have had the virus. It is known to have killed about 320,000. However, experts think the numbers may be underreported.
当前尚没有新冠肺炎的疗法或疫苗获得批准。已经有近480万人确诊感染该病毒。目前它已经导致32万人死亡。但是专家们认为该数字可能被低估了。

The World Health Organization has listed more than 100 efforts to develop effective treatments and vaccines for the coronavirus. The list includes clinical trials in China, at the University of Oxford, and with American drug makers Pfizer, Inovio and Moderna.
世卫组织列出了超过100项开发新冠病毒有效疗法和疫苗的工作研究计划。这份名单包括在中国、英国牛津大学、美国制药商辉瑞公司、Inovio公司以及现代公司进行的临床试验。

Experts predict a safe and effective vaccine could take 12 to 18 months to develop. The results of Moderna's early trial have not been published. But the news lifted the company's stock prices and spread hope that a solution against the infectious disease might be close.
专家预计开发出安全有效的疫苗可能需要12到18个月时间。现代公司早期试验结果尚未公布。但是这一消息提振了该公司的股价，并播撒了新冠肺炎解决方案即将面世的希望。

I'm Jonathan Evans.
我是乔纳森·埃文斯。

(51VOA.COM原创翻译，禁止转载，违者必究！)
