\href{https://www.51voa.com/VOA_Special_English/very-and-too-84302_1.html}{Article Translate} \\

This week we answer a question from Rafael.  He asks,
本周我们来回复拉斐尔提出的一个问题。他问道：
Question:
问题：

What's the difference between too and very?
"Very" 和 "too" 有什么区别？

Answer:
回复：

Dear Rafael,
亲爱的拉斐尔，

Thanks for asking this question. These words often cause problems for people who are learning English. That is because translating them into your own language may not give you a complete understanding of how they are used.
感谢你的提问。这些单词经常给正在学英语的人士造成麻烦。那是因为把它翻译成你自己的语言可能无法让你完全理解它们的用法。

"Very" and "too" are both adverbs. They come before an adjective.
"Very" 和 "too" 都是副词。它们都放在形容词前面。

The basic difference is that "very" emphasizes the word that follows it. "Too" before a word means there is more than what is wanted. You can see how this works clearly with the adjective "much" in these sentences:
最基本的区别是very是强调它后面所跟的单词。"Too"放在单词前面时的意思是指超出需求范围。你可以通过以下句子中much这个形容词来清楚地理解其用法。

I love chocolate very much. I eat one piece of chocolate a day.
我非常喜欢吃巧克力，我每天都吃一块巧克力。

He loves chocolate too much. He eats a whole box of chocolates every day.
他太喜欢吃巧克力了，他每天都要吃一整盒巧克力。

Very
非常

We use "very" to show there is a higher degree of some quality. It often appears in sentences with a positive meaning:
我们使用very来表示某些特质的更高程度。它通常出现了具有积极意义的句子里：

That is a very good movie.
那是一部非常好看的电影。

My dog is always very happy to see me.
我的狗见到我总是非常高兴。

Too
太

On the other hand, "too" means there is more of the quality than you want. This shows a negative idea. For example,
另一方面，too意味着该特质超出所需。这体现出一种消极的观点。例如，

That movie is too violent for me.
那部电影对我来说太暴力了。

What's the difference?
有什么不同呢？

The main difference between "very" and "too" is that using "too" suggests that there is some problem. On a really hard day, you might come home and say:
"Very" 和 "too" 的主要区别在于，使用too表明存在某些问题。在非常辛苦的一天，你回家后可能会说：

I am too tired to eat, so we should not go out for dinner.
我太累了不想吃饭，所以我们不要出去吃饭了。

On a better day, you might say:
在美好的一天，你可能会说：

I am very tired, but I can go out for dinner.
我很累，但是我可以出去吃饭。

Do you like Thai food? It has many spices. Someone who likes it would say:
你喜欢泰餐吗？它放了很多香料。喜欢吃泰餐的人会说：

I love Thai food: it is very spicy.
我喜欢吃泰餐：它非常辣。

Someone who does not like spices would say:
不喜欢各种香料的人士会说：

Thai food is too spicy.
泰餐太辣了（不喜欢吃）。

And that's Ask a Teacher for this week. Thank you very much for asking your question.
以上就是本周名师答疑的全部内容。非常感谢你的提问。

I'm Jill Robbins.
我是吉尔·罗宾斯。(51VOA.COM原创翻译，禁止转载，违者必究！)
