U.S. researchers on Monday gave the first shot to the first volunteer in a test for an experimental coronavirus vaccine. Scientists at the Kaiser Permanente Washington Health Research Institute in Seattle are carrying out the trial.
周一，美国研究人员对参与试验性冠状病毒疫苗测试的第一位志愿者进行了注射。西雅图市凯撒华州卫生健康研究所的科学家们正在进行这项试验。
"We're team coronavirus now," Kaiser Permanente scientist Dr. Lisa Jackson said.
凯撒华州卫生健康研究所的科学家莉莎·杰克逊表示：“我们现在开始驯服冠状病毒。”

The Associated Press watched the first volunteer, an employee of a small technology company, receive the injection. In total, the trial study will give 45 young, healthy volunteers two doses of the vaccine, one month apart.
美联社观察了首位志愿者接受疫苗注射的过程，这位志愿者是一家小型技术公司的雇员。这项试验性研究将为共计45位健康的年轻志愿者注射两剂疫苗，注射间隔为一个月。

Public health officials say it will take 12 to 18 months for a vaccine to be approved.
公共卫生官员表示，疫苗获批需要12到18个月时间。

The vaccine being tested in Seattle was developed by the U.S. National Institutes of Health and the biotechnology company Moderna. There is no chance the volunteers will get sickened from the vaccine; it does not contain the virus.
西雅图测试的这种疫苗是由美国国立卫生研究院和Moderna生物技术公司所研制。志愿者不会被疫苗感染，疫苗并不包含病毒。

The goal of the trial is only to make sure the vaccine does not have any worrisome side effects. Once it is proven to be safe, larger trials will begin.
这次试验的目的只是为了确保疫苗没有任何令人担忧的副作用。一旦安全性得到验证，就将会进行更大规模的试验。

Research groups around the world are working to create a vaccine for COVID-19, the disease caused by the new coronavirus. They are creating different kinds of vaccines. Some are shots developed from new technologies. These are faster to produce than traditional shots and may be stronger. Some research groups are even aiming for temporary vaccines, which would keep people safe for a month or two while longer-lasting protection is developed.
世界各地的研究小组都在努力开发针对新冠肺炎的疫苗。他们正在开发不同类型的疫苗。有些是采用新技术开发的针剂。与传统针剂相比，它们的生产速度更快，并且可能更强。一些研究小组甚至计划开发临时性疫苗，它将在长效疫苗开发期间给人们提供一到两个月的保护。

Next month, Inovio Pharmaceuticals will begin testing the safety of its vaccine in the American states of Pennsylvania and Missouri. Similar tests will then take place in China and South Korea.
下个月，诺维欧制药将会开始在美国宾夕法尼亚州和密苏里州测试其疫苗的安全性。随后中国和韩国也将进行类似的测试。

Even if early tests go well, "you're talking about a year to a year and a half" before any vaccine could be ready for widespread use, said Dr. Anthony Fauci. He is director of the NIH's National Institute of Allergy and Infectious Diseases.
安东尼·福西博士表示，即使早期测试进展顺利，任何疫苗广泛投入使用之前也需要一年到一年半时间。福西是美国国立卫生研究院国家过敏和传染病研究所所长。

Vaccine manufacturers are required to do additional studies on thousands of people to be sure a vaccine does not cause harm. But waiting is hard for the fearful public.
疫苗生产商必须对数千人进行进一步研究，以确保疫苗不会造成伤害。但是等待对恐慌民众来说是很艰难的。

U.S. President Donald Trump has been pushing for a vaccine. He recently said that the work is "moving along very quickly" and that he hoped to see a vaccine "soon."
美国总统川普一直在推动疫苗问世。他最近表示，这项工作进展很快，他希望很快看到疫苗问世。

There are no proven treatments for COVID-19. In China, scientists have been experimenting with HIV drugs as well as an experimental drug named remdesivir, which was created to fight Ebola.
目前针对新冠肺炎并没有被证实有效的疗法。在中国，科学家们一直在试验艾滋病药物，以及一种名为瑞德西韦、开发用于抗击埃博拉的试验性药物。

In the United States, the University of Nebraska Medical Center also began testing remdesivir in some Americans who were found to have COVID-19.
在美国，内布拉斯加大学医学中心也开始在一些感染新冠肺炎的美国患者身上测试瑞德西韦。

For most people, the new coronavirus causes mild sickness, including a fever and cough. But for older people and people with serious health problems, it can cause more severe illness, including pneumonia.
对大多数人来说，新冠病毒会引起包括发烧和咳嗽在内的轻度疾病。但是对老年人和本身患有严重疾病的人群来说，它会导致包括肺炎在内的更严重的疾病。

The worldwide outbreak has sickened more than 175,000 people and left more 6,000 dead.
新冠疫情全球爆发已经导致17.5万人感染，并造成6千多人死亡。

I'm Ashley Thompson.
我是阿什利·汤普森。(51VOA.COM原创翻译，禁止转载，违者必究！)